Usage metrics

### 2021-03-02 analysis/usage.Rmd
Expression coverage

cov_packages %>% ggplot() +
  geom_histogram(aes(x = coverage)) + 
  labs(x = "coverage (%)")

@@

>>>>

cov_packages %>% ggplot() +
  geom_histogram(aes(x = coverage), binwidth=1) + 
  labs(x = "coverage (%)")

@@

What is the actual coverage vs the expected coverage?
```{r}
expected_cov <- C_raw %>% select(package, coverage_expr) %>% 
  mutate(coverage_expr = replace_na(coverage_expr, 0)) %>% 
  mutate(coverage_expr = 100 * coverage_expr)

cov_diff <- expected_cov %>% left_join(cov_packages, by = "package") %>% 
  mutate(cdiff = pmax(0, coverage_expr - coverage))

cov_diff %>% ggplot() +
  geom_histogram(aes(x = cdiff), binwidth = 1) + 
  labs(x = "coverage difference (%)")
```

Most of the packages are in the first bin, where the difference is less than 1%, so the expression coverage is a good predictor of the actual `eval` coverage.
